Placeholder

### 2021-02-16 Paper_Histograms.Rmd
Ensured that each sign up month tibble has 3 rows, one for each sample

head(GLAD.retro_sign_up, 10)

>>>>

```{r Add extra rows to sign_up tibbles with only two samples}

sign_up_NBR_empty_row_April <- tibble(
  Sample_plot = "NBR",
  April = 0
)

sign_up_NBR_empty_row_August <- tibble(
  Sample_plot = "NBR",
  August = 0
)

sign_up_NBR_empty_row_September <- tibble(
  Sample_plot = "NBR",
  September = 0
)

dat.retro_april_sign_up <- dat.retro_april_sign_up %>% 
  rbind(sign_up_NBR_empty_row_April)

dat.retro_august_sign_up <- dat.retro_august_sign_up %>% 
  rbind(sign_up_NBR_empty_row_August)

dat.retro_september_sign_up <- dat.retro_september_sign_up %>% 
  rbind(sign_up_NBR_empty_row_September)
